---
title: "Create a simple map"
author: "Andres Felipe Lagos Ruiz"
date: "9/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This project was created as part of the Developing Data Products course of the Coursera Data Science Specialization. The goal of the project is to create a web page using R Markdown that features a map created with Leaflet, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

#Data Source

 * The site are from some Universities of Bogota - Colombia
 * The longitude and lantitude data was taken from Google Maps and Latitude Wesbsite
 
## proccess

```{r pressure, echo=FALSE}
# loading the library
library(leaflet)
# plotting the universities in the map
LatLong<-data.frame(
  lat = c(4.6281256, 4.6014634, 4.6420969),
  lng = c(-74.0677305, -74.0683221, -74.091785))

Names<- c('UNIVERSIDAD DISTRITAL FRANCISCO JOSÉ DE CALDAS', 'Universidad de los Andes',
          'Univeridad National of Colombia')

LatLong %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup = Names) #popup = puede inyectar urls
```


